---
title: "Analysis"
format: html
editor: visual
---

```{r}
install.packages("Matrix")
install.packages("psych")
install.packages("lmerTest")
install.packages("binom")

install.packages("broom.mixed")

```

```{r}
#DONE DEMOGRAPHICS
#| label: Demographics

library(tidyverse)
library(gtsummary)

data_ppt <- read.csv("../data/rawdata_participants.csv")
data_task <- read.csv("../data/rawdata_task.csv")

invisible(table(data_ppt$media_professional, useNA = "ifany"))

# Create demographics comparison table
demo_table <- data_ppt %>%
  select(
    media_professional,
    Gender,
    Age,
    Education,
    Discipline,
    Student,
    Ethnicity,
    Country
  ) %>%
  tbl_summary(
    by = media_professional,    # Group by TRUE vs FALSE
    missing = "no",
    type = list(Gender ~ "categorical")  # (optional safeguard)
  ) %>%
  add_p(
    test = all_continuous() ~ "wilcox.test",
    test.args = all_continuous() ~ list(exact = FALSE)  # <-- removed conf.int
  ) %>%
  modify_header(label ~ "Media Professional") %>%
  bold_labels()

demo_table


```

```{r}
#internal consistency BAIT Items
library(dplyr)
library(psych)

# Load
data_ppt <- read.csv("../data/rawdata_participants.csv")

# Reverse-coded items
rev_items <- c("BAIT_2_ImagesIssues", "BAIT_3_VideosIssues", 
               "BAIT_8_TextIssues", "BAIT_13_ArtIssues",
               "BAIT_9_Dangerous", "BAIT_10_Worry")

# Apply reverse scoring
data_ppt_rev <- data_ppt %>%
  mutate(across(all_of(rev_items), ~ 6 - ., .names = "{.col}_rev"))

# Now select only the final versions (reversed + original for positives)
bait_responses <- data_ppt_rev %>%
  transmute(
    BAIT_1_ImagesRealistic,
    BAIT_4_VideosRealistic,
    BAIT_5_ImitatingReality,
    BAIT_6_EnvironmentReal,
    BAIT_7_TextRealistic,
    BAIT_11_Exciting,
    BAIT_12_Benefit,
    BAIT_14_ArtRealistic,
    BAIT_2_ImagesIssues_rev,
    BAIT_3_VideosIssues_rev,
    BAIT_8_TextIssues_rev,
    BAIT_13_ArtIssues_rev,
    BAIT_9_Dangerous_rev,
    BAIT_10_Worry_rev
  )

# Cronbach's alpha
alpha_result <- psych::alpha(bait_responses)
alpha_result$total$raw_alpha  # overall alpha

# Omega
omega_result <- psych::omega(bait_responses, nfactors = 1)  
# nfactors=1 assumes unidimensional; you can also test multiple factors

```

```{r}
#Checking internal validity of BAIT Scale
library(psych)
library(dplyr)

# Load data
dat <- read.csv("../data/rawdata_participants.csv")

# Select only BAIT scale items (no AI Knowledge, AI Use, Attention Check)
bait_items <- dat %>%
  select(
    BAIT_1_ImagesRealistic,
    BAIT_2_ImagesIssues,
    BAIT_3_VideosIssues,
    BAIT_4_VideosRealistic,
    BAIT_5_ImitatingReality,
    BAIT_6_EnvironmentReal,
    BAIT_7_TextRealistic,
    BAIT_8_TextIssues,
    BAIT_9_Dangerous,
    BAIT_10_Worry,
    BAIT_11_Exciting,
    BAIT_12_Benefit,
    BAIT_13_ArtIssues,
    BAIT_14_ArtRealistic
  ) %>%
  mutate(across(everything(), ~as.numeric(as.character(.))))

# Cronbach’s alpha
alpha_result <- psych::alpha(bait_items, check.keys = TRUE)
print(alpha_result$total$raw_alpha)

# Omega
omega_result <- psych::omega(bait_items, nfactors = 1)
print(omega_result$omega.tot)

# KMO (use correlation matrix directly!)
kmo_result <- KMO(cor(bait_items, use = "pairwise.complete.obs"))
print(kmo_result)

```

```{r}
# ===== Stimulus validation using IDs directly from dat$Stimulus =====
library(dplyr)
library(tidyr)
library(lme4)

# 0) Safety + factor coding
stopifnot(all(c("Participant","Stimulus","aesthetic","emotional_expressive","Confidence_label") %in% names(dat)))

dat <- dat %>%
  filter(!is.na(Stimulus), !is.na(Participant)) %>%
  mutate(
    Stimulus    = factor(Stimulus),
    Participant = factor(Participant)
  )

# How many unique stimuli?
all_stims <- levels(dat$Stimulus)
length(all_stims)

# 1) Stimulus-level descriptives (via participant means first)
#    This avoids overweighting participants with more trials on a clip.
stim_desc <- dat %>%
  group_by(Stimulus, Participant) %>%
  summarise(
    m_aesthetic  = mean(aesthetic, na.rm = TRUE),
    m_emotion    = mean(emotional_expressive, na.rm = TRUE),
    m_confidence = mean(Confidence_label, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  group_by(Stimulus) %>%
  summarise(
    n_participants  = n(),                                # number of participants who rated this stimulus
    mean_aesthetic  = mean(m_aesthetic,  na.rm = TRUE),
    sd_aesthetic    = sd(m_aesthetic,    na.rm = TRUE),
    mean_emotion    = mean(m_emotion,    na.rm = TRUE),
    sd_emotion      = sd(m_emotion,      na.rm = TRUE),
    mean_confidence = mean(m_confidence, na.rm = TRUE),
    sd_confidence   = sd(m_confidence,   na.rm = TRUE),
    .groups = "drop"
  ) %>%
  arrange(Stimulus)

# Quick checks
nrow(stim_desc)                # should equal number of unique stimuli present in dat
summary(stim_desc$n_participants)

# 2) ICCs (stimulus-level reliability) via mixed models
#    ICC_stim = Var(Stimulus) / [Var(Stimulus) + Var(Residual)]
icc_from_model <- function(formula, data) {
  m <- lmer(formula,
            data = data,
            REML = TRUE,
            control = lmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 1e6)))
  vc <- as.data.frame(VarCorr(m))
  var_stim <- vc$vcov[vc$grp == "Stimulus"]
  var_res  <- vc$vcov[vc$grp == "Residual"]
  icc_stim <- var_stim / (var_stim + var_res)
  list(model = m, icc_stim = icc_stim)
}

icc_aesthetic <- icc_from_model(aesthetic ~ 1 + (1|Stimulus) + (1|Participant), dat)
icc_emotion   <- icc_from_model(emotional_expressive ~ 1 + (1|Stimulus) + (1|Participant), dat)
icc_conf      <- icc_from_model(Confidence_label ~ 1 + (1|Stimulus) + (1|Participant), dat)

cat("\n--- Stimulus ICCs (proportion of variance at stimulus level) ---\n")
cat(sprintf("Aesthetic:            ICC_stim = %.3f\n", icc_aesthetic$icc_stim))
cat(sprintf("Emotional/Expressive: ICC_stim = %.3f\n", icc_emotion$icc_stim))
cat(sprintf("Confidence (Task 2):  ICC_stim = %.3f\n", icc_conf$icc_stim))

# 3) Outlier detection at stimulus level (> 2 SD from stimulus mean distribution on any metric)
zflag <- function(x) (x - mean(x, na.rm = TRUE)) / sd(x, na.rm = TRUE)

stim_outliers <- stim_desc %>%
  mutate(
    z_aesthetic = zflag(mean_aesthetic),
    z_emotion   = zflag(mean_emotion),
    z_conf      = zflag(mean_confidence),
    outlier_any = abs(z_aesthetic) > 2 | abs(z_emotion) > 2 | abs(z_conf) > 2
  ) %>%
  filter(outlier_any) %>%
  arrange(Stimulus)

cat("\n--- Potential stimulus outliers (>2 SD on any metric) ---\n")
print(stim_outliers %>% select(Stimulus, starts_with("mean_"), starts_with("z_")))

# 4) Stimulus-level correlations (means across stimuli)
cor_mat <- stim_desc %>%
  select(mean_aesthetic, mean_emotion, mean_confidence) %>%
  cor(use = "pairwise.complete.obs")
cat("\n--- Stimulus-level correlations (means across stimuli) ---\n")
print(round(cor_mat, 3))

```

```{r}
#BAIT Desriptives Media vs non media
# --- Descriptives for BAIT scale ---

library(dplyr)
library(psych)
library(ggplot2)

# Load data
dat <- read.csv("../data/rawdata_participants.csv")

# 1. Select BAIT items (drop knowledge + attention check if present)
bait_items <- dat %>%
  select(starts_with("BAIT_")) %>%
  select(-matches("Knowledge|AttentionCheck|Use"))

# 2. Reverse-score negatively worded items 
# (so that higher = more negative toward AI)
negatively_worded <- c("BAIT_1_ImagesRealistic",   # realistic = positive → reverse
                       "BAIT_4_VideosRealistic",
                       "BAIT_5_ImitatingReality",
                       "BAIT_6_EnvironmentReal",
                       "BAIT_7_TextRealistic",
                       "BAIT_12_Benefit",
                       "BAIT_11_Exciting",
                       "BAIT_14_ArtRealistic")

# Make a copy and reverse (assuming scale 0–6)
bait_scored <- bait_items %>%
  mutate(across(all_of(negatively_worded), ~ 6 - .))

# 3. Compute composite (mean score, higher = more negative toward AI)
dat$BAIT_score <- rowMeans(bait_scored, na.rm = TRUE)

# 4. Descriptive statistics
summary(dat$BAIT_score)

# Histogram of AI attitude distribution
ggplot(dat, aes(x = BAIT_score)) +
  geom_histogram(binwidth = 0.5, fill = "#619CFF", color = "white") +
  labs(title = "Distribution of AI Attitudes",
       x = "BAIT Score (Higher = More Negative Toward AI)",
       y = "Count") +
  theme_minimal()

# 5. Group comparison: Media professionals vs Non-media
dat %>%
  group_by(media_professional) %>%
  summarise(
    mean_BAIT = mean(BAIT_score, na.rm = TRUE),
    sd_BAIT   = sd(BAIT_score, na.rm = TRUE),
    n         = n()
  )

t.test(BAIT_score ~ media_professional, data = dat)


```

```{r}
# aesthetic H1(a)

# Libraries
library(dplyr)
library(psych)
library(lme4)
library(lmerTest)    # adds p-values to lmer
library(emmeans)     # EMMs & contrasts
library(performance) # R2 etc.
library(conflicted)

# Resolve function-name conflicts for this session
conflicts_prefer(psych::alpha)   # alpha() = reliability
conflicts_prefer(lmerTest::lmer) # lmer() = lmerTest version

# --- Make items numeric (safe if they came in as factors/character) ---
data_task <- data_task %>%
  mutate(
    enjoyable = as.numeric(as.character(Enjoyable)),
    likeable  = as.numeric(as.character(Likeable)),
    pleasing  = as.numeric(as.character(Pleasing))
  )

# --- Reliability (Cronbach's alpha) ---
alpha_res <- psych::alpha(data_task[, c("enjoyable", "likeable", "pleasing")])
alpha_res  # prints full table
# If you want the number inline:
# alpha_res$total$raw_alpha

# --- Composite score ---
data_task <- data_task %>%
  mutate(aesthetic = rowMeans(dplyr::select(., enjoyable, likeable, pleasing), na.rm = TRUE))

# --- Prep analysis data ---
dat <- data_task %>%
  filter(!is.na(aesthetic), !is.na(Condition), !is.na(Participant), !is.na(Stimulus)) %>%
  mutate(
    Condition   = factor(Condition, levels = c("AI", "Human")), # AI = reference
    Participant = factor(Participant),
    Stimulus    = factor(Stimulus)
  )

# --- Mixed model (random intercepts for Participant & Stimulus) ---
m1 <- lmer(aesthetic ~ Condition + (1 | Participant) + (1 | Stimulus),
           data = dat, REML = FALSE)
summary(m1)

# --- Enable Satterthwaite df in emmeans for large N ---
emmeans::emm_options(
  pbkrtest.limit = nrow(dat),
  lmerTest.limit = nrow(dat),
  lmer.df        = "satterthwaite"  # be explicit
)

# --- Estimated marginal means and contrast (Human - AI) with Satterthwaite df ---
emm <- emmeans(m1, ~ Condition)
emm
contrast(emm, "revpairwise") %>% summary(infer = TRUE)

# --- (Optional) R2 for reporting ---
performance::r2(m1)

# --- (Optional) Random slopes by Participant; compare to m1 ---
m2 <- try(lmer(aesthetic ~ Condition + (1 + Condition | Participant) + (1 | Stimulus),
               data = dat, REML = FALSE))
if (!inherits(m2, "try-error")) {
  print(anova(m1, m2))  # chi-square test of fit improvement
  # If you decide to report m2 instead, you can get EMMs the same way:
  # emm2 <- emmeans(m2, ~ Condition)
  # contrast(emm2, "revpairwise") %>% summary(infer = TRUE)
}
# (You already fit m1 earlier)
# Ensure emmeans uses Satterthwaite df for large N
emmeans::emm_options(
  pbkrtest.limit = nrow(dat),
  lmerTest.limit = nrow(dat),
  lmer.df        = "satterthwaite"
)

# Estimated marginal means and contrast (now with df, not Inf)
emm <- emmeans::emmeans(m1, ~ Condition)
emm
emmeans::contrast(emm, "revpairwise") %>% summary(infer = TRUE)


# --- (Optional) Diagnostics ---
# check_model(m1)  # opens plots

```

```{r}
#emotional_expressive H1(b)

# Libraries
library(dplyr)
library(psych)
library(lme4)
library(lmerTest)    # adds p-values to lmer
library(emmeans)     # EMMs & contrasts
library(performance) # R2 etc.
library(conflicted)

# Resolve function-name conflicts for this session
suppressMessages({
  conflicts_prefer(psych::alpha)   # alpha() = reliability
  conflicts_prefer(lmerTest::lmer) # lmer() = lmerTest version
})

# --- Make items numeric (safe if factors/characters) ---
data_task <- data_task %>%
  mutate(
    emotional  = as.numeric(as.character(Emotional)),
    expressive = as.numeric(as.character(Expressive))
  )

# --- Reliability (Cronbach's alpha) ---
alpha_res_b <- psych::alpha(data_task[, c("emotional", "expressive")])
alpha_res_b  # prints full table
# alpha_res_b$total$raw_alpha  # if you want the value for reporting

# --- Composite score ---
data_task <- data_task %>%
  mutate(emotional_expressive = rowMeans(dplyr::select(., emotional, expressive), na.rm = TRUE))

# --- Prep analysis data ---
dat <- data_task %>%
  filter(!is.na(emotional_expressive), !is.na(Condition), !is.na(Participant), !is.na(Stimulus)) %>%
  mutate(
    Condition   = factor(Condition, levels = c("AI", "Human")), # AI = reference
    Participant = factor(Participant),
    Stimulus    = factor(Stimulus)
  )

# --- Mixed model (random intercepts for Participant & Stimulus) ---
m1 <- lmer(emotional_expressive ~ Condition + (1 | Participant) + (1 | Stimulus),
           data = dat, REML = FALSE)
summary(m1)

# --- Enable Satterthwaite df in emmeans for large N ---
emmeans::emm_options(
  pbkrtest.limit = nrow(dat),
  lmerTest.limit = nrow(dat),
  lmer.df        = "satterthwaite"
)

# --- Estimated marginal means and contrast (Human - AI) with Satterthwaite df ---
emm_b <- emmeans(m1, ~ Condition)
emm_b
contrast(emm_b, "revpairwise") %>% summary(infer = TRUE)

# --- (Optional) R2 for reporting ---
performance::r2(m1)

# --- (Optional) Random slopes by Participant; compare to m1 ---
m2 <- try(lmer(emotional_expressive ~ Condition + (1 + Condition | Participant) + (1 | Stimulus),
               data = dat, REML = FALSE))
if (!inherits(m2, "try-error")) {
  print(anova(m1, m2))  # chi-square test of fit improvement
  # If you decide to report m2 instead:
  # emm_b2 <- emmeans(m2, ~ Condition)
  # contrast(emm_b2, "revpairwise") %>% summary(infer = TRUE)
}

# --- (Optional) Diagnostics ---
# check_model(m1)  # opens plots

```

```{r}
#checking if top 25% emotional_expressive stims have different results
library(dplyr)
library(lme4)
library(lmerTest)
library(emmeans)

# 1. Create the composite score
data_task <- data_task %>%
  mutate(
    emotional_expressive = rowMeans(select(., Emotional, Expressive), na.rm = TRUE)
  )

# 2. Get average score per stimulus
stimulus_emotions <- data_task %>%
  group_by(Stimulus) %>%
  summarise(
    mean_emotion_expr = mean(emotional_expressive, na.rm = TRUE),
    .groups = "drop"
  )

# 3. Find stimuli with mean score >= 4
high_emotion_stimuli <- stimulus_emotions %>%
  filter(mean_emotion_expr >= 4) %>%
  pull(Stimulus)

# 4. Filter main data to just these stimuli
high_data <- data_task %>%
  filter(Stimulus %in% high_emotion_stimuli)

# 5. Fit mixed model on subset
m_high <- lmer(emotional_expressive ~ Condition + (1|Participant) + (1|Stimulus),
               data = high_data, REML = FALSE)

# Model summary
summary(m_high)

# 6. Estimated marginal means
emm_high <- emmeans(m_high, ~ Condition)
print(emm_high)

# 7. Difference with 95% CI
contrast(emm_high, method = "revpairwise") %>% summary(infer = TRUE)

```

```{r}
#official visual for H1a&b
# --- Refit H1a and H1b with distinct names, then plot violins/boxplots with EMM overlays ---

library(dplyr)
library(tidyr)
library(lme4)
library(lmerTest)
library(emmeans)
library(ggplot2)

# 0) Ensure composites exist (safe if already there)
data_task <- data_task %>%
  mutate(
    enjoyable  = as.numeric(as.character(Enjoyable)),
    likeable   = as.numeric(as.character(Likeable)),
    pleasing   = as.numeric(as.character(Pleasing)),
    aesthetic  = ifelse(is.na(aesthetic),
                        rowMeans(dplyr::select(., enjoyable, likeable, pleasing), na.rm = TRUE),
                        aesthetic),
    emotional  = as.numeric(as.character(Emotional)),
    expressive = as.numeric(as.character(Expressive)),
    emotional_expressive = ifelse(is.na(emotional_expressive),
                                  rowMeans(dplyr::select(., emotional, expressive), na.rm = TRUE),
                                  emotional_expressive),
    Condition   = factor(Condition, levels = c("AI","Human")),
    Participant = factor(Participant),
    Stimulus    = factor(Stimulus)
  )

# 1) Build separate analysis frames to avoid name clashes
dat_a <- data_task %>%
  filter(!is.na(aesthetic), !is.na(Condition), !is.na(Participant), !is.na(Stimulus))

dat_b <- data_task %>%
  filter(!is.na(emotional_expressive), !is.na(Condition), !is.na(Participant), !is.na(Stimulus))

# 2) Fit models with distinct names
m1a <- lmer(aesthetic ~ Condition + (1|Participant) + (1|Stimulus), data = dat_a, REML = FALSE)
m1b <- lmer(emotional_expressive ~ Condition + (1|Participant) + (1|Stimulus), data = dat_b, REML = FALSE)

# 3) EMMs (Satterthwaite df like before)
emmeans::emm_options(pbkrtest.limit = max(nrow(dat_a), nrow(dat_b)),
                     lmerTest.limit = max(nrow(dat_a), nrow(dat_b)),
                     lmer.df = "satterthwaite")

emm_a <- emmeans(m1a, ~ Condition) %>% as.data.frame() %>% mutate(Outcome = "Aesthetic")
emm_b <- emmeans(m1b, ~ Condition) %>% as.data.frame() %>% mutate(Outcome = "Emotional/Expressive")

emm_df <- bind_rows(emm_a, emm_b) %>%
  mutate(Condition = factor(Condition, levels = c("AI","Human")))

# 4) Long raw data for distributions
plot_df <- data_task %>%
  select(Condition, aesthetic, emotional_expressive) %>%
  pivot_longer(c(aesthetic, emotional_expressive),
               names_to = "Outcome", values_to = "Score") %>%
  filter(!is.na(Score)) %>%
  mutate(Outcome = recode(Outcome,
                          aesthetic = "Aesthetic",
                          emotional_expressive = "Emotional/Expressive"))

# 5) Colors
cond_cols <- c("AI" = "#1f77b4", "Human" = "#d62728")

# 6) Violin + boxplot + EMM overlays
p_violin <- ggplot(plot_df, aes(x = Condition, y = Score, fill = Condition, color = Condition)) +
  geom_violin(alpha = 0.20, trim = FALSE, linewidth = 0.4) +
  geom_boxplot(width = 0.20, outlier.alpha = 0.25, alpha = 0.55) +
  geom_pointrange(data = emm_df,
                  aes(x = Condition, y = emmean, ymin = lower.CL, ymax = upper.CL),
                  inherit.aes = FALSE, size = 1.1, fatten = 2, color = "black") +
  facet_wrap(~ Outcome, nrow = 1) +
  scale_fill_manual(values = cond_cols) +
  scale_color_manual(values = cond_cols) +
  labs(x = NULL, y = "Rating (0–6)",
       title = "Distributions by condition with model-estimated means (95% CI)") +
  theme_bw(base_size = 13) +
  theme(
    legend.position = "top",
    panel.grid.minor = element_blank(),
    panel.grid.major.x = element_blank(),
    strip.text = element_text(face = "bold"),
    plot.title = element_text(face = "bold")
  )

p_violin  # <--- print

# (Optional) Boxplot-only variant
p_box <- ggplot(plot_df, aes(x = Condition, y = Score, fill = Condition, color = Condition)) +
  geom_boxplot(width = 0.5, outlier.alpha = 0.25, alpha = 0.55) +
  geom_pointrange(data = emm_df,
                  aes(x = Condition, y = emmean, ymin = lower.CL, ymax = upper.CL),
                  inherit.aes = FALSE, size = 1.1, fatten = 2, color = "black") +
  facet_wrap(~ Outcome, nrow = 1) +
  scale_fill_manual(values = cond_cols) +
  scale_color_manual(values = cond_cols) +
  labs(x = NULL, y = "Rating (0–6)",
       title = "Boxplots by condition with model-estimated means (95% CI)") +
  theme_bw(base_size = 13) +
  theme(
    legend.position = "top",
    panel.grid.minor = element_blank(),
    panel.grid.major.x = element_blank(),
    strip.text = element_text(face = "bold"),
    plot.title = element_text(face = "bold")
  )

# p_box  # uncomment to show the boxplot version instead

```

```{r}
#visual comapre H1a and b
# If needed: install.packages("ggimage")
library(ggplot2)
library(ggimage)
library(dplyr)
library(emmeans)

# (Assumes you already have m_aesthetic/m_emoxpr from earlier code)
emm_a_obj <- emmeans(m_aesthetic, ~ Condition)
emm_b_obj <- emmeans(m_emoxpr,    ~ Condition)

emm_df <- bind_rows(
  as.data.frame(emm_a_obj) %>% mutate(Outcome = "Aesthetic"),
  as.data.frame(emm_b_obj) %>% mutate(Outcome = "Emotional/Expressive")
)

# Use PNG emoji icons instead of SVG (no rsvg dependency)
# Twemoji PNGs (72x72). If these ever 404, swap to a different PNG URL.
emm_df$image <- ifelse(
  emm_df$Condition == "Human",
  "https://cdnjs.cloudflare.com/ajax/libs/twemoji/14.0.2/72x72/1f464.png", # 👤
  "https://cdnjs.cloudflare.com/ajax/libs/twemoji/14.0.2/72x72/1f4bb.png"  # 💻
)

pos <- position_dodge(width = 0.6)

ggplot(emm_df, aes(x = Outcome, y = emmean, group = Condition)) +
  geom_errorbar(aes(ymin = lower.CL, ymax = upper.CL),
                position = pos, width = 0.12, linewidth = 0.5) +
  geom_image(aes(image = image), position = pos, size = 0.08) +
  scale_y_continuous(expand = expansion(mult = c(0.05, 0.12))) +
  labs(x = NULL, y = "Estimated marginal mean (0–6)",
       title = "Aesthetic Pleasure VS Emotionality/Expressivity: AI vs Human") +
  theme_classic(base_size = 14) +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 12, hjust = 1))


```

```{r}
#H2(a) Media Professionalism as moderator

library(dplyr)
library(lme4)
library(lmerTest)
library(emmeans)

# Make sure IDs are same type
data_task <- data_task %>% mutate(Participant = as.character(Participant))
data_ppt   <- data_ppt   %>% mutate(Participant = as.character(Participant))

# Merge TRUE/FALSE variable
dat <- data_task %>%
  left_join(
    data_ppt %>% select(Participant, media_professional),
    by = "Participant"
  ) %>%
  mutate(
    media_professional = ifelse(media_professional == TRUE, "Yes", "No"),
    media_professional = factor(media_professional, levels = c("No", "Yes")),
    Condition = factor(Condition, levels = c("AI", "Human")),
    Participant = factor(Participant),
    Stimulus = factor(Stimulus)
  )

# Function to run model
run_interaction_model <- function(dv) {
  message("=== Results for ", dv, " ===")
  form <- as.formula(paste(dv, "~ Condition * media_professional + (1|Participant) + (1|Stimulus)"))
  m <- lmer(form, data = dat, REML = FALSE)
  print(summary(m))
  
  emm <- emmeans(m, ~ Condition | media_professional)
  print(emm)
  print(contrast(emm, method = "revpairwise"))
}

# Run for aesthetic
run_interaction_model("aesthetic")

# Run for emotional_expressive
run_interaction_model("emotional_expressive")



```

```{r}
# --- Interaction plots for aesthetic & emotional_expressive (using your 'dat') ---

library(dplyr)
library(lme4)
library(lmerTest)
library(emmeans)
library(ggplot2)

# 1) Fit interaction models (Condition * media_professional) --------------------
m_aes <- lmer(aesthetic ~ Condition * media_professional + (1|Participant) + (1|Stimulus),
              data = dat, REML = FALSE)
m_emo <- lmer(emotional_expressive ~ Condition * media_professional + (1|Participant) + (1|Stimulus),
              data = dat, REML = FALSE)

# Use Satterthwaite df in emmeans (to match your reporting)
emmeans::emm_options(
  pbkrtest.limit = nrow(dat),
  lmerTest.limit = nrow(dat),
  lmer.df        = "satterthwaite"
)

# 2) EMMs by Condition within media_professional for both outcomes -------------
emm_aes <- emmeans(m_aes, ~ Condition | media_professional) %>%
  as.data.frame() %>% mutate(Outcome = "Aesthetic")

emm_emo <- emmeans(m_emo, ~ Condition | media_professional) %>%
  as.data.frame() %>% mutate(Outcome = "Emotional/Expressive")

emm_all <- bind_rows(emm_aes, emm_emo) %>%
  mutate(
    Condition = factor(Condition, levels = c("AI","Human")),
    media_professional = factor(media_professional, levels = c("No","Yes"))
  )

# 3) Two-panel interaction plot (main figure) ----------------------------------
p_interaction <- ggplot(emm_all,
                        aes(x = Condition, y = emmean,
                            group = media_professional, color = media_professional)) +
  geom_point(position = position_dodge(width = 0.30), size = 3) +
  geom_line(position = position_dodge(width = 0.30), linewidth = 1) +
  geom_errorbar(aes(ymin = lower.CL, ymax = upper.CL),
                width = 0.06, position = position_dodge(width = 0.30), linewidth = 0.9) +
  facet_wrap(~ Outcome, nrow = 1) +
  scale_color_manual(values = c("No" = "#1f77b4", "Yes" = "#d62728"),
                     name = "Media professional") +
  scale_y_continuous(limits = c(0, 6), expand = expansion(mult = c(0.02, 0.06))) +
  labs(x = NULL, y = "Estimated marginal mean (0–6)",
       title = "Interaction between label (AI vs Human) and media professionalism") +
  theme_bw(base_size = 13) +
  theme(legend.position = "top",
        strip.text = element_text(face = "bold"),
        plot.title = element_text(face = "bold", hjust = 0.5))

p_interaction

```

```{r}
# H2(b): BAIT x Label predicting Aesthetic & Emotional/Expressive
# - build BAIT_score inside the join so it always exists
# - ensure Condition/IDs are factors
# - fit models + plot side-by-side interactions

library(dplyr)
library(lme4)
library(lmerTest)
library(ggeffects)
library(ggplot2)
library(patchwork)

## 0) Make sure we have these in memory:
## dat      -> trial-level data with columns: Participant, Stimulus, Condition, aesthetic, emotional_expressive
## data_ppt -> participant-level data with BAIT_... columns

# standardize key
dat2      <- dat      %>% mutate(Participant = as.character(Participant))
data_ppt2 <- data_ppt %>% mutate(Participant = as.character(Participant))

# define BAIT columns to drop (if present)
bait_drop <- c("BAIT_AI_Knowledge","BAIT_AI_Use","BAIT_AttentionCheck")

# define *positively* framed items (reverse these so higher = more negative)
pos_items_all <- c(
  "BAIT_1_ImagesRealistic","BAIT_4_VideosRealistic","BAIT_5_ImitatingReality",
  "BAIT_6_EnvironmentReal","BAIT_7_TextRealistic","BAIT_11_Exciting",
  "BAIT_12_Benefit","BAIT_14_ArtRealistic"
)

# 1) Build BAIT_score inline, then join
dat_bait <- dat2 %>%
  left_join(
    data_ppt2 %>%
      # keep Participant + BAIT columns
      select(Participant, starts_with("BAIT_")) %>%
      # drop unwanted columns if they exist
      select(-any_of(bait_drop)) %>%
      # coerce all BAIT to numeric
      mutate(across(starts_with("BAIT_"), ~ as.numeric(as.character(.)))) %>%
      # reverse the "positive" items so higher = more negative attitude (0–6 assumed)
      {
        # only reverse those that exist
        pos_items <- intersect(pos_items_all, names(.))
        . %>% mutate(across(all_of(pos_items), ~ 6 - .))
      } %>%
      # compute BAIT_score (row mean across remaining BAIT)
      mutate(BAIT_score = rowMeans(select(., starts_with("BAIT_")), na.rm = TRUE)) %>%
      select(Participant, BAIT_score),
    by = "Participant"
  ) %>%
  # keep only rows that have a BAIT score
  filter(!is.na(BAIT_score)) %>%
  # set analysis factors
  mutate(
    BAIT_c      = as.numeric(scale(BAIT_score, center = TRUE, scale = FALSE)),
    Condition   = factor(Condition, levels = c("AI","Human")),
    Participant = factor(Participant),
    Stimulus    = factor(Stimulus)
  )

# quick sanity check (optional):
# stopifnot(all(c("aesthetic","emotional_expressive","Condition","Participant","Stimulus","BAIT_c") %in% names(dat_bait)))

# 2) Fit mixed models
m_aes <- lmer(aesthetic ~ BAIT_c * Condition + (1|Participant) + (1|Stimulus),
              data = dat_bait, REML = FALSE)

m_emo <- lmer(emotional_expressive ~ BAIT_c * Condition + (1|Participant) + (1|Stimulus),
              data = dat_bait, REML = FALSE)

# 3) Predictions for plots
pred_aes <- ggpredict(m_aes, terms = c("BAIT_c [all]", "Condition"))
pred_emo <- ggpredict(m_emo, terms = c("BAIT_c [all]", "Condition"))

# 4) Side-by-side interaction plots
pal <- c("AI" = "#1f77b4", "Human" = "#d62728")

p1 <- ggplot(pred_aes, aes(x = x, y = predicted, color = group, fill = group)) +
  geom_line(size = 1.2) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = 0.15, color = NA) +
  scale_color_manual(values = pal, name = "Initial label") +
  scale_fill_manual(values = pal,  name = "Initial label") +
  labs(x = "BAIT score (centered; higher = more negative)",
       y = "Predicted aesthetic rating",
       title = "Aesthetic ~ BAIT × Label") +
  theme_minimal(base_size = 13) +
  theme(plot.title = element_text(face = "bold"))

p2 <- ggplot(pred_emo, aes(x = x, y = predicted, color = group, fill = group)) +
  geom_line(size = 1.2) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = 0.15, color = NA) +
  scale_color_manual(values = pal, name = "Initial label") +
  scale_fill_manual(values = pal,  name = "Initial label") +
  labs(x = "BAIT score (centered; higher = more negative)",
       y = "Predicted emotional/expressive rating",
       title = "Emotional/Expressive ~ BAIT × Label") +
  theme_minimal(base_size = 13) +
  theme(plot.title = element_text(face = "bold"))

p1 + p2


```

```{r}
# Identify unusually long completion times

# Calculate median and IQR
median_time <- median(data_ppt$Experiment_Duration, na.rm = TRUE)
iqr_time <- IQR(data_ppt$Experiment_Duration, na.rm = TRUE)

# Set threshold (here: more than 3×IQR above the median)
upper_threshold <- median_time + 3 * iqr_time

# Flag participants above threshold
data_ppt$long_time_flag <- data_ppt$Experiment_Duration > upper_threshold

# View flagged participants
long_takers <- data_ppt %>% 
  filter(long_time_flag == TRUE)

# Convert to minutes
data_ppt$time_elapsed_min <- data_ppt$Experiment_Duration / 60000

# Check summary
summary(data_ppt$Experiment_Duration_min)

# Print flagged participants
print(long_takers)

# Summary count of who is flagged
table(data_ppt$long_time_flag)

# Check threshold value for reference
upper_threshold

```

```{r}
# H3: Are media professionals more confident? (Satterthwaite df output)

library(dplyr)
library(lme4)
library(lmerTest)
library(emmeans)

# Ensure IDs match type
data_task <- data_task %>% mutate(Participant = as.character(Participant))
data_ppt  <- data_ppt  %>% mutate(Participant = as.character(Participant))

# Merge media_professional into main dataset & create absolute confidence variable
dat <- data_task %>%
  left_join(
    data_ppt %>% select(Participant, media_professional),
    by = "Participant"
  ) %>%
  mutate(
    media_professional = factor(ifelse(media_professional == TRUE, "Yes", "No"),
                                levels = c("No", "Yes")),
    Condition    = factor(Condition, levels = c("AI", "Human")),
    Participant  = factor(Participant),
    Stimulus     = factor(Stimulus),
    # make sure Confidence_label is numeric, then distance from midpoint (0–3)
    Confidence_label = as.numeric(as.character(Confidence_label)),
    confidence_abs   = abs(Confidence_label - 3)
  )

# Enable Satterthwaite df like in H1/H2
emmeans::emm_options(
  pbkrtest.limit = nrow(dat),
  lmerTest.limit = nrow(dat),
  lmer.df        = "satterthwaite"
)

# Mixed model: Confidence by Condition and Media Professional status
m_conf <- lmer(confidence_abs ~ Condition * media_professional +
                 (1 | Participant) + (1 | Stimulus),
               data = dat, REML = FALSE)

# Model summary (now with t and df)
summary(m_conf)

# Estimated marginal means per Condition within media_professional
emm <- emmeans(m_conf, ~ Condition | media_professional)
emm

# Label effect (Human - AI) within each group, with 95% CI and Satterthwaite df
contrast(emm, "revpairwise") %>% summary(infer = TRUE)

```

```{r}
# ---- H3 interaction plot: Confidence by Condition × Media professionalism ----
library(ggplot2)
library(dplyr)

# Turn EMMs into a tidy data frame
emm_df <- as.data.frame(emm) %>%
  mutate(
    Condition = factor(Condition, levels = c("AI","Human")),
    media_professional = factor(media_professional, levels = c("No","Yes"))
  )

# Colors (consistent with earlier figures)
pro_cols <- c("No" = "#1f77b4", "Yes" = "#d62728")

p_h3 <- ggplot(emm_df,
               aes(x = Condition, y = emmean,
                   color = media_professional, group = media_professional)) +
  geom_point(position = position_dodge(width = 0.30), size = 3) +
  geom_line(position = position_dodge(width = 0.30), linewidth = 1) +
  geom_errorbar(aes(ymin = lower.CL, ymax = upper.CL),
                width = 0.06, position = position_dodge(width = 0.30),
                linewidth = 0.9) +
  scale_color_manual(values = pro_cols, name = "Media professional") +
  # confidence_abs ranges 0–3, so lock the axis for interpretability
  scale_y_continuous(limits = c(0, 3), expand = expansion(mult = c(0.02, 0.06))) +
  labs(x = NULL,
       y = "Confidence (distance from midpoint; 0–3)",
       title = "H3: Confidence by label (AI vs Human) and media professionalism (EMMs ±95% CI)") +
  theme_bw(base_size = 13) +
  theme(legend.position = "top",
        strip.text = element_text(face = "bold"),
        plot.title = element_text(face = "bold", hjust = 0.5))

p_h3

```

```{r}
library(dplyr)
library(lme4)
library(lmerTest)
library(emmeans)

# Ensure correct coding
dat <- dat %>%
  mutate(
    Condition   = factor(Condition, levels = c("AI", "Human")), # Task 1 label
    Participant = factor(Participant),
    Stimulus    = factor(Stimulus)
  )

# -----------------
# Identify unsure responses (rating == 3)
# -----------------
dat <- dat %>%
  mutate(
    unsure = Confidence_label == 3,
    category_task2 = case_when(
      Confidence_label <= 2 ~ "AI",
      Confidence_label >= 4 ~ "Human",
      TRUE ~ NA_character_
    ),
    category_task2 = factor(category_task2, levels = c("AI", "Human")),
    match = ifelse(!is.na(category_task2) & category_task2 == Condition, 1, 0)
  )

# Count unsure responses
unsure_count <- sum(dat$unsure, na.rm = TRUE)
unsure_pct <- round(unsure_count / nrow(dat) * 100, 2)

cat("Number of unsure responses excluded:", unsure_count, "\n")
cat("Percentage of total responses excluded:", unsure_pct, "%\n")

# -----------------
# 1. Confidence model (all data, including unsure)
# -----------------
m_conf <- lmer(Confidence_label ~ Condition + (1|Participant) + (1|Stimulus),
               data = dat, REML = FALSE)
summary(m_conf)

emm_conf <- emmeans(m_conf, ~ Condition)
contrast(emm_conf, method = "revpairwise") %>% summary(infer = TRUE)

# -----------------
# 2. Matching model (unsure excluded)
# -----------------
dat_match <- dat %>% filter(!is.na(match))

m_match <- glmer(match ~ Condition + (1|Participant) + (1|Stimulus),
                 data = dat_match, family = binomial)
summary(m_match)

emm_match <- emmeans(m_match, ~ Condition, type = "response")
contrast(emm_match, method = "revpairwise") %>% summary(infer = TRUE)

```

```{r}
library(dplyr)
library(ggplot2)

# --- Helper to pick the first existing column name
pick_col <- function(df, candidates) {
  hits <- intersect(candidates, names(df))
  if (length(hits) == 0) stop("None of the candidate columns found: ", paste(candidates, collapse=", "))
  hits[1]
}

# ---- Confidence EMMs (usually columns: emmean, lower.CL, upper.CL)
conf_df_raw <- as.data.frame(emm_conf)
conf_y   <- pick_col(conf_df_raw, c("emmean"))
conf_lcl <- pick_col(conf_df_raw, c("lower.CL"))
conf_ucl <- pick_col(conf_df_raw, c("upper.CL"))

conf_df <- conf_df_raw %>%
  mutate(Condition = factor(Condition, levels = c("AI","Human"))) %>%
  transmute(
    Condition,
    y    = .data[[conf_y]],
    ymin = .data[[conf_lcl]],
    ymax = .data[[conf_ucl]]
  )

# ---- Match EMMs (binomial; columns often: prob, asymp.LCL, asymp.UCL)
match_df_raw <- as.data.frame(emm_match)
match_y   <- pick_col(match_df_raw, c("prob","emmean","response"))
match_lcl <- pick_col(match_df_raw, c("asymp.LCL","lower.CL"))
match_ucl <- pick_col(match_df_raw, c("asymp.UCL","upper.CL"))

match_df <- match_df_raw %>%
  mutate(Condition = factor(Condition, levels = c("AI","Human"))) %>%
  transmute(
    Condition,
    y    = .data[[match_y]],
    ymin = .data[[match_lcl]],
    ymax = .data[[match_ucl]]
  )

# Palette
cond_cols <- c("AI" = "#1f77b4", "Human" = "#d62728")

# ===== Panel A: Confidence — Violin + Box + EMM overlay =====
p_conf_violin <- ggplot(dat, aes(x = Condition, y = Confidence_label, fill = Condition, color = Condition)) +
  geom_violin(trim = FALSE, alpha = 0.18, linewidth = 0.5, na.rm = TRUE) +
  geom_boxplot(width = 0.16, outlier.alpha = 0.25, alpha = 0.45, na.rm = TRUE) +
  geom_pointrange(
    data = conf_df,
    aes(x = Condition, y = y, ymin = ymin, ymax = ymax),
    inherit.aes = FALSE, color = "black", size = 0.9
  ) +
  scale_fill_manual(values = cond_cols) +
  scale_color_manual(values = cond_cols) +
  scale_y_continuous(limits = c(0, 6), expand = expansion(mult = c(0.02, 0.06))) +
  labs(x = NULL, y = "Confidence rating (0–6)",
       title = "Confidence by initial label (raw distribution + model EMM)") +
  theme_bw(base_size = 13) +
  theme(legend.position = "none",
        plot.title = element_text(face = "bold", hjust = 0.5))

# ===== Panel B: Match — participant-level means + EMM probability overlay =====
# Compute participant-level mean match per condition (reduces stacking at 0/1)
dat_match_summary <- dat_match %>%
  group_by(Participant, Condition) %>%
  summarise(match_mean = mean(match, na.rm = TRUE), .groups = "drop")

p_match_jitter <- ggplot() +
  # participant means (jittered)
  geom_jitter(
    data = dat_match_summary,
    aes(x = Condition, y = match_mean, color = Condition),
    width = 0.18, height = 0.02, alpha = 0.45, size = 2, na.rm = TRUE
  ) +
  # model-estimated probability + 95% CI (black)
  geom_pointrange(
    data = match_df,
    aes(x = Condition, y = y, ymin = ymin, ymax = ymax),
    inherit.aes = FALSE, color = "black", size = 0.9
  ) +
  scale_color_manual(values = cond_cols) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1),
                     limits = c(0, 1), expand = expansion(mult = c(0.02, 0.06))) +
  labs(x = NULL, y = "Match to initial label (proportion)",
       title = "Match by initial label (participant means + model probability)") +
  theme_bw(base_size = 13) +
  theme(legend.position = "none",
        plot.title = element_text(face = "bold", hjust = 0.5))

# Combine (if patchwork available)
if (requireNamespace("patchwork", quietly = TRUE)) {
  library(patchwork)
  (p_conf_violin | p_match_jitter) +
    plot_annotation(
      title = "H4(a): Distributions (left) and model-estimated effects (black) for confidence & match",
      theme = theme(plot.title = element_text(face = "bold", size = 15, hjust = 0.5))
    )
} else {
  print(p_conf_violin); print(p_match_jitter)
}

```

```{r}
# H5(a): Does emotional_expressive predict "more human" confidence differently by label?

library(dplyr)
library(lme4)
library(lmerTest)
library(emmeans)

# Prepare dataset (center emo; keep units on original scale)
dat_int <- dat %>%
  mutate(
    emo_c      = scale(emotional_expressive, center = TRUE, scale = FALSE),
    Condition  = factor(Condition, levels = c("AI","Human")),
    Participant = factor(Participant),
    Stimulus    = factor(Stimulus)
  )

# Main & interaction models
m_main_emo <- lmer(
  Confidence_label ~ emo_c + Condition + (1 | Participant) + (1 | Stimulus),
  data = dat_int, REML = FALSE
)
m_int_emo <- lmer(
  Confidence_label ~ emo_c * Condition + (1 | Participant) + (1 | Stimulus),
  data = dat_int, REML = FALSE
)

# Model comparison (does the interaction add value?)
anova(m_main_emo, m_int_emo)

# Summary of interaction model
summary(m_int_emo)

# Use Satterthwaite df for emmeans (avoid 'Inf' df)
emmeans::emm_options(
  pbkrtest.limit = nrow(dat_int),
  lmerTest.limit = nrow(dat_int),
  lmer.df        = "satterthwaite"
)

# Simple slopes of emo_c within each Condition
slopes <- emtrends(m_int_emo, ~ Condition, var = "emo_c")
summary(slopes)  # slopes (per 1-unit increase in emotional_expressive)

# Difference between slopes (AI vs Human)
slope_diff <- contrast(slopes, "pairwise") %>% summary(infer = TRUE)
slopes
slope_diff

```

#visual rep

library(ggplot2)

library(dplyr)

\# Create prediction data from your fitted model

pred_data \<- ggeffects::ggpredict(m_int_emo, terms = c("emo_c \[all\]", "Condition"))

\# Plot

ggplot(pred_data, aes(x = x, y = predicted, color = group)) +

geom_line(size = 1.2) +

geom_ribbon(aes(ymin = conf.low, ymax = conf.high, fill = group), alpha = 0.15, color = NA) +

labs(

x = "Emotionality Rating (centered)",

y = "Predicted Task 2 Confidence Rating",

color = "Initial Label",

fill = "Initial Label",

title = "Interaction Between Emotionality and Initial Label on Task 2 Confidence"

) +

scale_color_manual(values = c("#619CFF", "#F8766D")) +

scale_fill_manual(values = c("#619CFF", "#F8766D")) +

theme_minimal(base_size = 14)

```{r}
# Visual: interaction between emotionality and initial label on confidence
library(ggeffects)   # <-- needed for ggpredict
library(ggplot2)
library(dplyr)

# Make sure the factor order matches your analysis (AI = reference)
dat_int <- dat_int %>%
  mutate(Condition = factor(Condition, levels = c("AI","Human")))

# Predictions from the fitted interaction model
pred_data <- ggeffects::ggpredict(m_int_emo, terms = c("emo_c [all]", "Condition"))
# pred_data has columns: x, predicted, conf.low, conf.high, group

ggplot(pred_data, aes(x = x, y = predicted, color = group)) +
  geom_line(linewidth = 1.1) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high, fill = group),
              alpha = 0.18, color = NA) +
  scale_color_manual(values = c("AI" = "#1f77b4", "Human" = "#d62728"), name = "Initial label") +
  scale_fill_manual(values = c("AI" = "#1f77b4", "Human" = "#d62728"),  name = "Initial label") +
  scale_y_continuous(limits = c(0, 6), expand = expansion(mult = c(0.02, 0.06))) +
  labs(
    x = "Emotional/Expressive (centered)",
    y = "Predicted confidence (0–6)",
    title = "H5(b): Emotional/expressive and Predicted Label"
  ) +
  theme_minimal(base_size = 14) +
  theme(plot.title = element_text(face = "bold"))

```

```{r}
# H5(b): Does Aesthetic × Condition predict Task-2 confidence?

library(dplyr)
library(lme4)
library(lmerTest)
library(emmeans)
library(ggplot2)

# 0) Prep (AI as reference; center, not scale, to keep units interpretable)
dat_int <- dat %>%
  mutate(
    aesthetic_c = scale(aesthetic, center = TRUE, scale = FALSE),
    Condition   = factor(Condition, levels = c("AI","Human")),
    Participant = factor(Participant),
    Stimulus    = factor(Stimulus)
  )

# 1) Fit models (main-effects vs. interaction)
m_main <- lmer(
  Confidence_label ~ aesthetic_c + Condition + (1|Participant) + (1|Stimulus),
  data = dat_int, REML = FALSE
)

m_int <- lmer(
  Confidence_label ~ aesthetic_c * Condition + (1|Participant) + (1|Stimulus),
  data = dat_int, REML = FALSE
)

# 2) Model comparison (does the interaction improve fit?)
anova(m_main, m_int)

# 3) Summary with Satterthwaite df
emmeans::emm_options(
  pbkrtest.limit = nrow(dat_int),
  lmerTest.limit = nrow(dat_int),
  lmer.df        = "satterthwaite"
)
summary(m_int)

# 4) Simple slopes (slope of aesthetic_c within each Condition)
slopes <- emtrends(m_int, specs = "Condition", var = "aesthetic_c")
slopes
contrast(slopes, "pairwise") %>% summary(infer = TRUE)

# 5) Build prediction grid for plotting (EMMs across the range of aesthetic_c)
a_range <- with(dat_int, seq(min(aesthetic_c, na.rm = TRUE),
                             max(aesthetic_c, na.rm = TRUE), length.out = 100))

pred_df <- emmeans(m_int, ~ aesthetic_c | Condition,
                   at = list(aesthetic_c = a_range)) %>%
  as.data.frame()

# Be robust to emmeans column names
# (typically: emmean, lower.CL, upper.CL; but we'll guard anyway)
pick_col <- function(df, candidates) {
  hits <- intersect(candidates, names(df))
  if (!length(hits)) stop("Could not find any of: ", paste(candidates, collapse=", "))
  hits[1]
}
y_col   <- pick_col(pred_df, c("emmean","response","prob","predicted"))
lcl_col <- pick_col(pred_df, c("lower.CL","asymp.LCL","conf.low"))
ucl_col <- pick_col(pred_df, c("upper.CL","asymp.UCL","conf.high"))

plot_df <- pred_df %>%
  mutate(Condition = factor(Condition, levels = c("AI","Human"))) %>%
  transmute(
    Condition,
    aesthetic_c = aesthetic_c,
    pred  = .data[[y_col]],
    lower = .data[[lcl_col]],
    upper = .data[[ucl_col]]
  )

# 6) Plot (same style/colors as earlier figures)
cond_cols <- c("AI" = "#1f77b4", "Human" = "#d62728")

p_aesthetic <- ggplot(plot_df, aes(x = aesthetic_c, y = pred, color = Condition, fill = Condition)) +
  geom_line(linewidth = 1.1) +
  geom_ribbon(aes(ymin = lower, ymax = upper), alpha = 0.18, color = NA) +
  scale_color_manual(values = cond_cols, name = "Initial label") +
  scale_fill_manual(values = cond_cols,  name = "Initial label") +
  scale_y_continuous(limits = c(0, 6), expand = expansion(mult = c(0.02, 0.06))) +
  labs(
    x = "Aesthetic rating (centered)",
    y = "Predicted confidence (0–6)",
    title = "Aesthetic Rating & Label Bias"
  ) +
  theme_minimal(base_size = 14) +
  theme(plot.title = element_text(face = "bold"))

p_aesthetic

```
